---
title: "Learned Index Structure Dataset AMZ2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DescTools)
```

## R Markdown

```{r echo=FALSE}
knitr::read_chunk('HelperFunction_LIndex.R')
```

Reading the data and then drawing the plot

```{r readData}
amz <- read.csv(file = "datasets/amz_salepooint_000721393X_com_norm.csv")
str(amz)
attach(amz)
```


```{r fitPolynomial, echo=TRUE, eval=FALSE}
<<Polyfit_amz>>
func_fitPoly(X,amz)
```

Based on the fitting, degree 4 polynomial seems suiitable

```{r PolyVisual, echo=TRUE}
<<Polyfit_Visual>>
Quadfunct = func_PolyVis(X,4,date,amz)
```

### Step 2: Residual visualization
```{r ResidualVisual}

plot(Quadfunct$residuals^2)
ultraMax <- which.max(Quadfunct$residuals^2)
print(Quadfunct$residuals[ultraMax]^2)

#Attack 36@4700 when lastN=60
#attack 192@3500 when lastN=60, CUSUM=6
maxQ <- which(Quadfunct$residuals^2>3500)
#Max k residuals
#print(maxQ)
print(maxQ)
print(length(maxQ))
points(maxQ,Quadfunct$residuals[maxQ]^2, col="green",cex=2,pch=20)
```


### Step 3: Raw data analysis without using the model

```{r keydiffVisual}
<<key_diff_visual>>
  keyDiff <- func_keyDiff(X,date)
  keyDim <- dim(keyDiff)[1]
```

### Step 4: Fitting normal distribution on KeyDiff
CUSUM algorithm is based on the assumption that the underlying algorithm follows a normal distribution. We thus fit a Gaussian curve on the keyDiff data.

```{r GausFit}
<<GaussFit>>
  FIT <- func_FitNorm(keyDiff)
```


### STEP 5: CUSUM implementation
```{r CUSUMCall}
<<CUSUM_Impl2>>
outcomeExits = func_CUSUM2(FIT,6,keyDiff,keyDim,y_lim=70000)
print(outcomeExits)

<<PlotRes>>
  func_plotRes(Quadfunct,maxQ,ultraMax)


```

### Step 6: Evaluation 1
```{r evaluation1, eval=TRUE}
<<Evaluation1>>
lastN=60
EvalMeasure = func_eval1(lastN,keyDim,Quadfunct,maxQ,outcomeExits)
print(EvalMeasure)
```
Proportion of relevant points extracted (TODO) 


#### Step 6: Evaluation 2
```{r evaluation2, eval=TRUE}

<<Evaluation2>>
EvalMeasure2 = func_eval2(outcomeExits,keyDim,lastN)
print(EvalMeasure2)
```

Ratio of points visited


### Step 7: 2 sided CUSUM and evaluation
```{r CUSUMCall2sided}

<<CUSUM_Impl3>>
<<CUSUM_Wrapper>>
#attack 192@3500 when lastN=100, CUSUM=6 -> 156
outcomeExits = func_CUSUM_wrapper(FIT,6,keyDiff,keyDim,y_lim=70000)

print(outcomeExits)
<<PlotRes>>
  func_plotRes(Quadfunct,maxQ,ultraMax)

lastN=100
EvalMeasure = func_eval1(lastN,keyDim,Quadfunct,maxQ,outcomeExits)
print(EvalMeasure)

(EvalMeasure2 = func_eval2(outcomeExits,keyDim,lastN))

```



### 8 Grid Search
```{r GridSearch,warning=FALSE,eval=FALSE}

lastN = seq(10,200,by = 10)
T_factor = seq(3,7,by = 0.5)
eval1 = data.frame(matrix(1:90,ncol=9))
eval2 = data.frame(matrix(1:90,ncol=9))

for (l in 1:20){
  for (t in 1:9){
    outcomeExits = func_CUSUM_wrapper(FIT,T_factor[t],keyDiff,keyDim,y_lim=70000,FALSE)
    eval1[l,t] = func_eval1(lastN[l],keyDim,Quadfunct,maxQ,outcomeExits,FALSE)
    eval2[l,t] = func_eval2(outcomeExits,keyDim,lastN[l])
  }
}

names(eval1) <- T_factor
names(eval2) <- T_factor
row.names(eval1) <- lastN
row.names(eval2) <- lastN

print(eval1)
print(eval2)

matplot(eval1,type = "l")
matplot(eval2,type = "l")

detach(amz)


```

